brados: declarative, programmable object storage

### 2016-05-25 paper.tex
make sentence shrt
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

%%% why is it hard / why do naive approaches fail
In addition to the growth in the quantity of operations in use throughout Ceph
installations, Figure~\ref{fig:objclass-dev} also depicts the amount of
low-level C++ written to implement these operations. Unfortunately, this code
is written assuming a performance profile defined by the combination of the
hardware and software versions available at the time of development.  While
the bulk of these interfaces are created by core Ceph developers with a
complete view of the performance model, this may be changing as the
development community has been receptive to outside contributions with the
recent inclusion by CERN developers of an extension for performing limited
numeric operations on object data~\cite{cls_numops}. And while Ceph has not
yet reached the point of directly exposing these features to
non-administrative users, the inclusion of a mechanism for dynamically
defining extensions using Lua~\cite{cls_lua} (currently pending review)
suggests that aspects of this
feature may soon appear. What is needed is support for creating storage
interfaces using a method that allows transparent optimization as the system,
application, and supporting environment evolve.

>>>>

%%% why is it hard / why do naive approaches fail
In addition to the growth in the quantity of operations in use throughout Ceph
installations, Figure~\ref{fig:objclass-dev} also depicts the amount of
low-level C++ written to implement these operations. Unfortunately, this code
is written assuming a performance profile defined by the combination of the
hardware and software versions available at the time of development.  While
the bulk of these interfaces are created by core Ceph developers with a
complete view of the performance model, this may be changing. The
development community has been receptive to outside contributions with the
recent inclusion by CERN developers of an extension for performing limited
numeric operations on object data~\cite{cls_numops}. And while Ceph has not
yet reached the point of directly exposing these features to
non-administrative users, the inclusion of a mechanism for dynamically
defining extensions using Lua~\cite{cls_lua} (currently pending review)
suggests that aspects of this
feature may soon appear. What is needed is support for creating storage
interfaces using a method that allows transparent optimization as the system,
application, and supporting environment evolve.
